\documentclass[]{resume-openfont}
\definecolor{boldone}{HTML}{FF0000}
\definecolor{primary1}{HTML}{F15A29}
\definecolor{primary2}{HTML}{F7941D}
\definecolor{primary3}{HTML}{00A0E0}
\definecolor{primary5}{HTML}{8C2A75}
\definecolor{primary4}{HTML}{59CD83}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\namesection{Nicky Semenza}{full-stack software engineer}{ \href{mailto:nicky@nickysemenza.com}{nicky@nickysemenza.com} \\
\href{http://nickysemenza.com}{nickysemenza.com} \\
408-396-4786
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.26\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\textcolor{primary1}{Education}}

\subsection{Purdue University}
\descript{BS in Computer Science}
Conc. in Software Engineering \\
\location{Expected May 2018 \\ West Lafayette, IN}
\sectionsep


\descript{The Harker School}
\location{May 2014 | San Jose, CA}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\textcolor{primary2}{Coursework}}
Data Mining\\
Machine Learning\\
Web Search Management\\
Information Retreival\\ 
Operating Systems \\
Software Testing \\
Systems Programming \\
Computer Architecutre \\ 
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{\textcolor{primary4}{Skills}}
% % \subsection{Languages}
% \location{Proficient:}
% PHP \textbullet{}   JavaScript \textbullet{} Python \textbullet{} React.js \\
% HTML \textbullet{} CSS \textbullet{} Node.js \textbullet{} SQL \\ 
% \location{Skilled:}
% golang \textbullet{} C \textbullet{} C++ \textbullet{} Angular \textbullet{} R \\
% \location{Tools + Infrastructure:}
% git \textbullet{} docker \textbullet{} redis \textbullet{} nginx \textbullet{} AWS\\
% \location{Creative:}
% Sketch \textbullet{} Illustrator \textbullet{} Photoshop
% \sectionsep
\section{\textcolor{primary3}{Skills}}
\runsubsection{Proficient:}
PHP, JavaScript, Python, React.js, HTML, CSS, Node.js, SQL\\
\sectionsep \sectionsep
\runsubsection{Skilled:}
golang, C, C++, Angular, R\\
\sectionsep \sectionsep
\runsubsection{Tools + Infrastructure:}
git, docker, redis, nginx, AWS\\
\sectionsep \sectionsep
\runsubsection{Creative:}
Sketch, Illustrator, Photoshop\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     HACKATHON PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\textcolor{primary4}{Hackathon Projects}}
\runsubsection{HackIllinois}
  QRBlast - transferring data via QR codes.\\
  \location{Android,  Python}
  \sectionsep \sectionsep
\runsubsection{PennApps}
  Taskr - Local marketplace for college students.\\
  \location{Mongo, Angular, Express}
\sectionsep \sectionsep
\runsubsection{MHacks}
   Facevid - Face swapping on live video.\\
   \location{Python, OpenCV }
\sectionsep \sectionsep
\runsubsection{BoilerMake}
   Picspace - Location based collaborative drawing. \\
   \location{Firebase, Laravel}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\textcolor{primary5}{Links}}
\href{https://github.com/nickysemenza}{github.com/\custombold{nickysemenza}} \\
\href{https://www.linkedin.com/in/nickysemenza}{linkedin.com/in/\custombold{nickysemenza}} \\
\href{https://twitter.com/nickysemenza}{twitter.com/\custombold{nickysemenza}} \\
\href{https://nickysemenza.com}{nickysemenza.com} \\
\href{https://nicky.photos}{nicky.photos} \\
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.7\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{SmugMug}
\descript{| Software Engineering Intern }
\location{May 2017 – Aug 2017 | Mountain View, CA | React.js, PHP}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Worked on modernizing video playback infrastructure from Flash to HLS Streaming.
\item Rewrote many consumer pages in React whilst updating the UI to conform to updated styles.
\end{tightemize}
\sectionsep

\runsubsection{Parachute.co}
\descript{| Software Engineer}
\location{Oct 2014 – Dec 2016 | remote | PHP, Laravel, Angular.js, Ionic}
\begin{tightemize}
\item Developed and deployed a PHP-powered backend API from the ground up to support mobile apps + web.
\item Created a consumer facing frontend UI as well as administration tooling.
\end{tightemize}
\sectionsep

\runsubsection{SmugMug}
\descript{| Software Engineering Intern }
\location{May 2016 – Aug 2016 | Mountain View, CA | PHP, YUI, React.js}
\begin{tightemize}
\item Added functionality to the e-commerce portion of customer’s SmugMug sites to enable custom phone cases to be sold.
\item Worked on migrating the billing system to allow purchasing and fulfillment of SmugMug monthly subscriptions in the customer's native currency.
\end{tightemize}
\sectionsep

\runsubsection{Indiana State Chemist}
\descript{| Software Engineering Intern}
\location{Sept 2014 – May 2015 | West Lafayette, IN | PHP, JavaScript}
\begin{tightemize}
\item Contributed to the development of a full-stack CMS for both internal agricultural testing workflows and public record lookup.
\item Developed a javascript powered based single page application coupled with a PHP powered backend.
\end{tightemize}
\sectionsep

% \runsubsection{Purdue Exponent Newspaper}
% \descript{| Photojournalist}
% \location{Sept 2014 – Present | West Lafayette, IN}
% \begin{tightemize}
% \item Photography of sports games, performances, and campus events for online and printed media.
% \item Production of video pieces to accompany articles.
% \end{tightemize}
% \sectionsep

\runsubsection{Endorse}
\descript{| Software Engineering Intern}
\location{Jun 2012 - Feb 2013 | San Mateo, CA | }
\begin{tightemize}
\item Designed and executed test plans for mobile devices.
\item Wrote Python-based scrapers to extract UPC codes from retailer websites.
\item Helped tune the OpenCV based OCR pipeline for grocery receipt scanning.
\end{tightemize}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Leadership
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\textcolor{black}{Leadership + Projects}}
\runsubsection{BoilerMake Hackathon}
\descript{| Event Organizer + Developer}
\location{Apr 2015 – Present | \href{https://github.com/boilermake}{github.com/boilermake}}
\begin{tightemize}
\item Worked with a group of 20 students to organize an annual hackathon with 500+ students in attendance from around the country and a \$200K budget
\item Oversaw a development team that built an applicant review system using PHP and React, as well as other internal tooling
\end{tightemize}
\sectionsep

\runsubsection{Purdue Computer Science}
\descript{| CS190 Teaching Assistant}
\location{Aug 2015 - Dec 2015 | Purdue University}
\begin{tightemize}
\item TA for lab sections of CS Tools course, which helps freshman learn the basics of shells, version control, UNIX, etc, as well as providing helpful  productivity tips and tricks
\item Contributed to the open source curriculum for the course
\end{tightemize}
\sectionsep

\runsubsection{Recipe Hub}
\descript{| \href{https://github.com/nickysemenza/food}{github.com/nickysemenza/food}}
\location{2017-2018 | golang, React.js, AWS}
\begin{tightemize}
\item Tool that scrapes, analyzes, and displays a user's Facebook Message conversation history.
\end{tightemize}

\runsubsection{Antelope}
\descript{| \href{https://github.com/nickysemenza/antelope}{github.com/nickysemenza/antelope}}
\location{2017 | PHP, laravel, React.js, AWS}
\begin{tightemize}
\item Open source collaborative email inbox for teams.
\end{tightemize}

\runsubsection{Spit Cards}
\descript{| \href{https://github.com/nickysemenza/spit}{github.com/nickysemenza/spit}}
\location{2017-2018 | Node.js, React.JS, sockets}
\begin{tightemize}
\item Live multi-player implementation of the popular card game `spit'
\end{tightemize}

\runsubsection{Message Analyzer}
\descript{| \href{https://github.com/nickysemenza/message-analyzer}{github.com/nickysemenza/message-analyzer}}
\location{2017 | Node.JS, React, MongoDB}
\begin{tightemize}
\item Tool that scrapes, analyzes, and displays a user's Facebook Message conversation history.
\end{tightemize}

\sectionsep

\end{minipage} 
\end{document}